---
title: 'Reproducible Research: Peer Assessment 1'
author: "Matias"
date: "Sunday, March 15, 2015"
output:
  html_document:
    keep_md: yes
    theme: spacelab
---

##Loading and preprocessing the data.

```{r}
#Load the data
activity<-read.table("C:/Users/Usuario/Downloads/Reproducible Research/activity.csv", 
           header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
````


##Exploring the data.
```{r}

names(activity)

summary(activity)

#Number of NA's
table(is.na(activity))

````

##What is mean total number of steps taken per day?
```{r}
steps = rep(0,nlevels(activity$date))
for( i in 1:nlevels(activity$date)) {
        tot = activity[activity$date == levels(activity$date)[i],] 
        steps[i] = sum(tot$steps)
}
steps =cbind(steps, levels(activity$date))
num_steps=as.numeric(steps[,1])


mn<-mean(na.omit(num_steps))
md<-median(na.omit(num_steps))

steps_per_day <- aggregate(activity[,c("steps"), drop=FALSE],
                           by=list(date=activity$date), FUN=sum)
hist(steps_per_day$steps)

```
The mean total number of steps taken per day is `r mean(na.omit(num_steps))` and the median is
`r md`

##What is the average daily activity pattern?

```{r} 

#Filling the NA`s values with the mean for that interval.
library(dplyr)
#Creating a new data set
activity1=activity
for(i in 1:length(activity1$steps)) if (is.na(activity$steps[i])){  
   activity1$steps[i] = mean(filter(tm1, interval==activity1$interval[i])$steps)
}
hist(activity1$steps)

mn2<-mean((activity1$steps))
md2<-median((activity1$steps))
```      
The mean total number of steps taken per day is `r mn2` and the median is
`r md2`
```{r}
#Para ver cantidad de pasos por intervalo


#Grouping by interval
by_interval <- tm1 %>% group_by(interval)
#Takes the mean of steps by interval
plot_by_interval <- by_interval %>% summarise_each(funs(mean),steps)
#Plot
plot(plot_by_interval$interval, plot_by_interval$steps, type="l")
````
#Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
plot_by_interval[plot_by_interval$steps==max(plot_by_interval$steps),]
```

```{r}
 
#Removes NA's from activity

tm1<-activity[!is.na(activity$steps),]

summary(tm1)

```

```{r}

#Para calcular el número de pasos por día
s = rep(0,nlevels(tm1$date))
for( i in 1:nlevels(tm1$date)) {
        tv = tm1[tm1$date == levels(tm1$date)[i],] 
        s[i] = sum(tv$steps)
}
s =cbind(s, levels(tm1$date))
```

```{r echo=FALSE}  
tab<-as.data.frame(s)
tab$steps=tab[,1]
tab$date=tab[,2]
tab[,1]=NULL
tab[,1]=NULL
```
The number of steps taken each day is
```{r}
tab
```


###Histogram of the total number of steps taken each day
```{r}
hist(as.numeric(s[,1]))
```
The number of NA's in the data set is 2304 
```{r} 
table(is.na(activity))  
```



```{r}
#Transform date
activity1[,4]<-as.Date(activity1$date)
activity1[,4]<-weekdays(activity1[,4])

#Creates variable days
for (i in 1:nrow(activity1)) {if(activity1[i,4] == "sábado" 
                                | activity1[i,4] == "domingo") 
                        activity1$days[i] = "weekend"
                       
                           if(activity1[i,4] == "lunes" 
                              | activity1[i,4] == "martes"
                              | activity1[i,4] == "miércoles" 
                              | activity1[i,4] == "jueves" 
                              | activity1[i,4] == "viernes")
                         activity1$days[i] = "weekday"
                        }
#Transform variable days to factor
activity1$days = factor(activity1$days)
library("ggplot2")
qplot(interval, steps, data=activity1, facets=days~., geom="path")
```
